The Ky Fan Norms and Beyond: Dual Norms and Combinations for Matrix Optimization

### 2025-09-24 conf_article/neon.tex
prepared the article to be commented on

\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\newtheorem{lemma}{Lemma}
\newcommand{\norm}[1]{\lVert #1\rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

@@

%\icompfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

\usepackage{arydshln} % dashed lines

@@

\section{Introduction}
 Minimizing loss functions in unprecedentedly high-dimensional spaces has recently become an integral and crucial part in training large language models. Hence, new scalable, time- and memory-efficient algorithms have been demanded. Besides well-known Adam \citep{kingma2014adam} and AdamW \citep{loshchilov2017decoupled}, recently proposed Muon \citep{jordan2024muon} has shown promising results on training very large models \citep{liu2025muon}. Its key difference from Adam and AdamW is that it has been constructed specifically for optimizing functions of weight matrices, which are common in deep learning.

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{changes}
\definechangesauthor[name={Ivan Kozyrev}, color=orange]{IK}
\newtheorem{lemma}{Lemma}
\newcommand{\norm}[1]{\lVert #1\rVert}
\newcommand{\abs}[1]{\lvert #1 \rvert}

@@

\icompfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

\usepackage{arydshln} % dashed lines
\usepackage[right=5cm, marginparwidth=4.6cm, marginparsep=0.2cm]{geometry} % For comments!

@@

\section{Introduction}
This is the original text. \added[id=IK, comment={I think we should mention this.}]{This is a new sentence that has been added.}

 Minimizing loss functions in unprecedentedly high-dimensional spaces has recently become an integral and crucial part in training large language models. Hence, new scalable, time- and memory-efficient algorithms have been demanded. Besides well-known Adam \citep{kingma2014adam} and AdamW \citep{loshchilov2017decoupled}, recently proposed Muon \citep{jordan2024muon} has shown promising results on training very large models \citep{liu2025muon}. Its key difference from Adam and AdamW is that it has been constructed specifically for optimizing functions of weight matrices, which are common in deep learning.
